### 2019-10-15 article.tex
abstract added

%%%Author definitions
\def\tsc#1{\csdef{#1}{\textsc{\lowercase{#1}}\xspace}}
\tsc{WGM}
\tsc{QE}
\tsc{EP}
\tsc{PMS}
\tsc{BEC}
\tsc{DE}
%%%

\begin{document}
\let\WriteBookmarks\relax
\def\floatpagepagefraction{1}
\def\textpagefraction{.001}
\shorttitle{Leveraging social media news}
\shortauthors{CV Radhakrishnan et~al.}

\title [mode = title]{This is a specimen $a_b$ title}                      
\tnotemark[1,2]

\tnotetext[1]{This document is the results of the research
   project funded by the National Science Foundation.}

\tnotetext[2]{The second title footnote which is a longer text matter
   to fill through the whole text width and overflow into
   another line in the footnotes area of the first page.}

\author[1,3]{CV Radhakrishnan}[type=editor,
                        auid=000,bioid=1,
                        prefix=Sir,
                        role=Researcher,
                        orcid=0000-0001-7511-2910]
\cormark[1]
\fnmark[1]
\ead{cvr_1@tug.org.in}
\ead[url]{www.cvr.cc, cvr@sayahna.org}

@@

\address[1]{Elsevier B.V., Radarweg 29, 1043 NX Amsterdam, The Netherlands}

\author[2,4]{Han Theh Thanh}[style=chinese]

\author[2,3]{CV Rajagopal}[%
   role=Co-ordinator,
   suffix=Jr,
   ]
\fnmark[2]
\ead{cvr3@sayahna.org}
\ead[URL]{www.sayahna.org}

\credit{Data curation, Writing - Original draft preparation}

\address[2]{Sayahna Foundation, Jagathy, Trivandrum 695014, India}

\author%
[1,3]
{Rishi T.}
\cormark[2]
\fnmark[1,3]
\ead{rishi@stmdocs.in}
\ead[URL]{www.stmdocs.in}

\address[3]{STM Document Engineering Pvt Ltd., Mepukada,
    Malayinkil, Trivandrum 695571, India}

\cortext[cor1]{Corresponding author}
\cortext[cor2]{Principal corresponding author}
\fntext[fn1]{This is the first author footnote. but is common to third
  author as well.}
\fntext[fn2]{Another author footnote, this is a very long footnote and
  it should be a really long footnote. But this footnote is not yet
  sufficiently long enough to make two lines of footnote text.}

\nonumnote{This note has no numbers. In this work we demonstrate $a_b$
  the formation Y\_1 of a new type of polariton on the interface
  between a cuprous oxide slab and a polystyrene micro-sphere placed
  on the slab.
  }

\begin{abstract}
This template helps you to create a properly formatted \LaTeX\ manuscript.

\noindent\texttt{\textbackslash begin{abstract}} \dots 
\texttt{\textbackslash end{abstract}} and
\verb+\begin{keyword}+ \verb+...+ \verb+\end{keyword}+ 
which
contain the abstract and keywords respectively.

\noindent Each keyword shall be separated by a \verb+\sep+ command.
\end{abstract}

@@

\begin{keywords}
quadrupole exciton \sep polariton \sep \WGM \sep \BEC
\end{keywords}

>>>>

\input{mymacros.tex}

\begin{document}
\let\WriteBookmarks\relax
\def\floatpagepagefraction{1}
\def\textpagefraction{.001}
\shorttitle{Bayesian classification of Parkinson's disease patients using fMRI data}
\shortauthors{Amin Amini, Mayam Amirmazlaghani}

\title [mode = title]{Bayesian classification of Parkinson's disease patients using fMRI data}

\author[1]{Maryam Amirmazlaghani}
\cormark[1]
\ead{mazlaghani@aut.ac.ir}

\author[1]{Amin Amini}
\ead{amin-amini@aut.ac.ir}

@@

\address[1]{Department of Computer Engineering and Information Technology, Amirkabir University of Technology, Tehran, Iran}

\cortext[cor1]{Corresponding author}

\begin{abstract}
The goal of resting-state functional magnetic resonance imaging (fMRI) is to investigate the brain's functional connections by using the temporal similarity between blood oxygenation level dependent (BOLD) signals in different regions of the brain “at rest” as an indicator of synchronous neural activity.
However having different images of patients brain despite the sequential time based information, may contain enough data to investigate their brain and enable us to recognize some diseases.
In this paper, we propose a novel method to automatically extract these non time sequence base information using a Bayesian deep learning algorithm based on convolutional neural network.
Instead of using some predefined points of interest (POIs) we use the whole data in training phase so those points of the brain which do not contain related information about the disease will be ignored automatically by the trained model.
Moreover this method do not takes any assumptions based on disease, patients, etc.,
makes it a possible universal disease diagnosis approach to differentiate diseases having an impact on brain functionality.
This method is a supervised algorithm with small amount of calculations based on three dimensional convolutional network .
Each fMRI scan (which contains {\it t} time slices of brain) of patients will divided into {\it t} different 3D images enabling us to make our dataset much bigger in number and calculations way simpler.
Subsequently all of these image are fed to a network similar to LeNet-5 (but in three dimensions) to train our model.
Then to determine if a person is suffering from Parkinson's or not, we test his/her {\it t} fMRI images and get {\it t} different results which leads to a fraction (probability) of how healthy his/her brain is and if that fraction is above 0.5 we can classify that sample as Parkinson's patient.
\end{abstract}

@@

\begin{keywords}
Functional magnetic resonance imaging (fMRI) \sep
Resting-state \sep
Disease diagnosis \sep
Bayesian deep learning \sep
Convolutional neural network (CNN)
\end{keywords}
